A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/theor-experiment.tex
fig ref
starting to edit theor-exp

In this section we present numerical results of the validation benchmark and
  discuss optimization of a photoinjector operated in the space charge dominated regime.

@@

As expected, the x dimension is impacted by the bending elements, and unable to reach 
the small beam sizes seen in the y dimension. This suggest suggests objectives in the x 
dimension will drive design variable choices used in operations. 
However, it is still necessary to 
include the y dimension in the optimization. Early optimization tests showed the y dimension 
can easily grow out of control if it is not included in the objectives.
Those results are not shown here due to the unfeasible nature of the solutions 
(i.e. $rms_y$ larger than the beam pipe).
In the case of bunch length, there are not many options to choose from.
Ignoring the extreme value on the right, Fig.~\ref{fig:pareto2} shows the 
range of optimal bunch lengths fall between 1.39 and 1.5 mm.

>>>>

In this section a numerical results of the validation benchmark and
  optimization of a photoinjector operated in the space charge dominated regime is presented.

@@

As expected, the x dimension is impacted by the bending elements, and unable to reach 
the small beam sizes seen in the y dimension. This suggest suggests objectives in the x 
dimension will drive design variable choices used in operations. 
However, it is still necessary to 
include the y dimension in the optimization. Early optimization tests showed the y dimension 
can easily grow out of control if it is not included in the objectives.
Those results are not shown here due to the unfeasible nature of the solutions 
(i.e. $rms_y$ larger than the beam pipe).
In the case of bunch length, there are not many options to choose from.
Ignoring the extreme value on the right, Fig.~\ref{fig:pareto1} shows the 
range of optimal bunch lengths fall between 1.39 and 1.5 mm.
